Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/abstraction_desiderata.tex
Some commits

We propose the following two desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
\begin{enumerate}
\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller \dnote{requires further info}. In general, \acp{MDP} of interest that are intractable are typically made so in virtue of the size of their state space, not the size of the action space or transition model.
\item \textsc{Optimality}: To induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
\end{enumerate}

@@

Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space $S_1$, which consists of a single (arbitrary) state from $S_G$. Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.

@@

The interesting case is satisfying {\it both} desiderata. To the best of our knowledge, no theory of temporal abstraction sufficiently satisfies the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.

>>>>

We propose the following two desiderata on theories of abstraction in the context of planning or learning, given a Markov Decision Process, $M_G$:
\begin{enumerate}
\item \textsc{Compressibility}: To compress $M_G$ to be significantly smaller. \footnote{where smallness is understood as defined in the of \cite{LITTMAN COMPLEXITY}  blah blah blah}
\item \textsc{Optimality}: To induce an MDP $M_A$ such that solving $M_A$ basically solves $M_G$.
\end{enumerate}

@@

Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state from $S_G$. Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.

@@

The interesting case is satisfying {\it both} desiderata. To the best of our knowledge, no theory of temporal abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata.

### 2016-04-30 icml_workshop/introduction.tex
Some commits

\dnote{Abstraction pitch}
% Introduce a pitch about abstraction that's a bit different from our other paper.
Intelligent agents that leverage abstraction may reason about just the salient features of their environment, while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.

@@

In this work, we propose two desiderata on theories of abstraction in the context of planning or learning in an \ac{MDP}; the first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}, while the second we coin \textsc{Optimality}, stating that abstractions ought to maintain at least some notion of optimality. We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata. In light of these desiderata, we propose a formal framework that allows for simple state-abstraction methods as well as extension to temporal abstractions. We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata. Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions. We argue that the present state of the literature is inconclusive as to the effectiveness of options in general, and that, the theory of temporal abstraction afforded by the state aggregation approach allows for the satisfaction of both \textsc{Compressibility} and \textsc{Optimality}. We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.

>>>>

\dnote{Abstraction pitch}
% Introduce a pitch about abstraction that's a bit different from our other paper.
Intelligent agents that leverage abstraction may reason about just the salient features of their environment, while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat only fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues, we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.%This is the paragraph from ICML 2016

@@

In this work, we propose two desiderata on theories of abstraction in the context of planning or learning in an \ac{MDP}; the first we call \textsc{Compressibility}, which stipulates that a theory on abstraction ought to achieve {\it compression}, while the second we coin \textsc{Optimality}, stating that abstractions ought to maintain at least some notion of optimality. We defend these desiderata briefly in the next section, and describe the status of current work relative to these two desiderata.

In light of these desiderata, we summarize a formal framework that allows for simple state-abstraction methods as well as propose an extension to temporal abstractions. \enote{Summarize the formal abstraction bit -- MDP} We summarize the current state of the art theoretical results under this framework and describe how this framework satisfies both desiderata. Moreover, a central goal of this work is to illuminate future work on options and temporally extended actions. We argue that the present state of the literature is inconclusive as to the effectiveness of options in general, and that, the theory of temporal abstraction afforded by the state aggregation approach allows for the satisfaction of both \textsc{Compressibility} and \textsc{Optimality}. We offer a description of this framework, as well as preliminary empirical results, and paths to relevant analysis.

%
